### 2022-09-28 LaTeX/MSGARCH.tex
Adds murphydiagrams

\usepackage{cleveref}
\usepackage{acronym}
\usepackage[toc,page]{appendix}
\usepackage{subfig}
\graphicspath{{./img/}}
\usepackage{caption}

% ACRONYMS 
\newacro{GARCH}{General Autoregressive Conditional Heteroskedasticity}
\newacro{ARCH}{Autoregressive Conditional Heteroskedasticity}
\newacro{ARMA}{AutoRegressive Moving Average}
\newacro{SGED}{Skewed Generlized Error Distribution}
\newacro{GED}{Generlized Error Distribution}
\newacro{MSE}{mean-square error}
\newacro{MAE}{mean-absolute error}
\newacro{RMSE}{root-mean-square error}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% List of Symbols %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{List of Symbols} 
\addcontentsline{toc}{section}{Symbol directory}
\noindent Include a symbol directory if you use more than three uncommon abbreviations.
	\begin{tabular}{l l}
		\textbf{} & \\
		$\pi$ & rate of inflation\\
		$i$ & nominal interest rate \\
		$r$ & real interest rate \\
		$M$ & money stock \\

	\end{tabular}\\ \vspace{1cm}

@@

\section{Background}

@@

$$ \mathcal{L}\left(\Psi \mid \mathcal{I}_T\right) \equiv \prod_{t=1}^T f\left(y_t \mid \Psi, \mathcal{I}_{t-1}\right) $$ 
\subsection{Markov-Switching Models}

@@

\subsection{Financial Market Data}

@@

\subsubsection{Heavy-tailed Distributions}
Many different distributions have been suggested for modeling asset returns, among them the log-normal, students-t and the \ac{GED} and stable tempered distributions.
In this paper we will use the \ac{GED}, given the difficulty of implementing algorithms using more advanced distributions such as the stable tempered.
$$f_{\mathrm{GED}}(\eta ; \nu) \equiv \frac{\nu e^{-\frac{1}{2}|\eta / \lambda|^\nu}}{\lambda 2^{(1+1 / \nu)} \Gamma(1 / \nu)}, \quad \lambda \equiv\left(\frac{\Gamma(1 / \nu)}{4^{1 / \nu} \Gamma(3 / \nu)}\right)^{1 / 2}$$

@@

The general Markov-switching GARCH specification we use follows \cite{ardia_markov-switching_2019}: 
Denote $y_t$ the log-returns in time period $t$, i.e. $log(p_t-p_{t-1})$ if $p_t$ is the asset price at time t.

@@

@@

\subsection{Data set}
The GARCH model assumes that the datapoints are equidistant in the time dimension, hence we will use the closing prices of the Index and model the close-to-close variance. Both for numerical reasons as well as for the ease of interpretation we will use the log-returns multiplied by 100 for training the model and for the evaluation.

@@

\subsection{Results}
\subsubsection{Analysis of Model Behaviour and Parameters}
In \cref{tab:model-params} the model parameters for the (MS-)GARCH model (see \cref{eq:GJR}) and shape parameters $\Psi = (\nu, \xi)$ of the conditional distribution (see ) are displayed, which were fitted using a maximum likelihood estimator on the training set. 
The two separate states from the MSGARCH model are denoted MSSR1 and MSSR2.
%TODO: Describe characteristics of MSSR1, MSSR2 and GARCH.
XXXX is likely to play a role after large volatility spikes like the 1987 Black Monday (see XXXX).

% latex table generated in R 4.1.2 by xtable 1.8-4 package
% Tue Sep 27 12:14:13 2022
\vspace{0.5cm}
\begin{minipage}[c]{0.5\textwidth}
	\begin{tabular}{rrrr}
		\hline
		& MSSR1 & MSSR2 & GARCH \\ 
		\hline
		$\alpha_{0,1}$ & 0.0042 & 0.1680 & 0.0082 \\ 
		$\alpha_{1,1}$ & 0.0214 & 0.0168 & 0.0356 \\ 
		$\alpha_{2,1}$ & 0.0781 & 0.2072 & 0.0741 \\ 
		$\beta_1$ & 0.9347 & 0.7483 & 0.9207 \\ 
		$\nu_1$ & 1.5314 & 1.0446 & 1.3168 \\ 
		$\xi_1$ & 0.9680 & 0.8731 & 0.9329 \\ 
		\hline
	\end{tabular}
	\captionof{table}{Fitted model and shape parameters.}
	 \label{tab:model-params}
\end{minipage}
\begin{minipage}[c]{0.5\textwidth}
	\begin{tabular}{lrr} 
		\hline
		& $t+1 | k=1$ & $t+1 | k=2$ \\
		\hline
		$t | k=1$ & 0.9983 & 0.0017 \\
		$t | k=2$ & 0.0059 & 0.9941 \\
		\hline
	\end{tabular}
	\captionof{table}{Transitions probabilities of the MSGARCH states.}
 	\label{tab:trans-probs}
\end{minipage}
\vspace{0.5cm}

In \cref{tab:trans-probs} the transitions probabilities for the states in the MSGARCH model are displayed. The stable probabilities (i.e. the long-term probability of being in state 1 or 2) are XXXX for MSSR1 and XXXX for MSSR2.

@@

\subsubsection{Evaluation of Point Forecasts}

@@

@@

\begin{appendices}
\chapter{Point Forecasts}
\label{app:point-forecasts}

>>>>

\usepackage{cleveref}
\usepackage{acronym}
\usepackage[toc,page]{appendix}
%\usepackage{subfig}
\graphicspath{{./img/}}
\usepackage{caption}
\usepackage[yyyymmdd]{datetime}
\usepackage{subcaption}
%\usepackage[demo]{graphicx}

% ACRONYMS 
\newacro{GARCH}{General Autoregressive Conditional Heteroskedasticity}
\newacro{ARCH}{Autoregressive Conditional Heteroskedasticity}
\newacro{ARMA}{AutoRegressive Moving Average}
\newacro{SGED}{Skewed Generlized Error Distribution}
\newacro{GED}{Generalized Error Distribution}
\newacro{MSE}{mean-square error}
\newacro{MAE}{mean-absolute error}
\newacro{RMSE}{root-mean-square error}
\newacro{MSM}{Markov-Switching Model}
\newacro{HMM}{Hidden Markov Model}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% List of Symbols %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{List of Symbols} 
\addcontentsline{toc}{section}{Symbol directory}
\noindent Include a symbol directory if you use more than three uncommon abbreviations.
	\begin{tabular}{l l}
		\textbf{} & \\
		$\sigma$ & standard deviation\\
		$\Psi$ & set of parameter values \\
		$h$ conditional variance
	\end{tabular}\\ \vspace{1cm}

@@

\section{Background}
\subsection{Markov-Switching Models}
The general model consists of two stochastic processes $X$ and $Y$. The process $Y$ is observed, e.g. the stock price of a company, and it's conditional distribution depends on the unobserved Markov chain process $X$. According to \cite{an_identifiability_2013}, when the distribution of $y_t$ depends only on $x_t$ it is called a \ac{HMM}, and if it additionally depends  on the lagged values $y_{t-1}, ... y_{t-l}$ we call it a \ac{MSM}.

@@

$$ \mathcal{L}\left(\Psi \mid \mathcal{I}_T\right) \equiv \prod_{t=1}^T f\left(y_t \mid \Psi, \mathcal{I}_{t-1}\right) $$

@@

\subsection{Financial Markets}

@@

\subsubsection{Distributions}
Many different distributions have been suggested for modeling asset returns and volatility, among them the log-normal, students-t and the \ac{GED} and stable tempered distributions. 
In this paper we will consider the (Log-)normal, the \ac{GED} and the Student-t distribution, given the difficulty of implementing algorithms using more advanced distributions such as the stable tempered distribution. The following three distributions are in standardized form, i.e. they are centered around 0 and have a standard deviation of 1.

\paragraph{Normal Distribution}
$$f_N(\eta) \equiv \frac{1}{\sqrt{2 \pi}} e^{-\frac{1}{2} \eta^2}$$

\paragraph{Generalized Error Distribution}
$$f_{\mathrm{GED}}(\eta ; \nu) \equiv \frac{\nu e^{-\frac{1}{2}|\eta / \lambda|^\nu}}{\lambda 2^{(1+1 / \nu)} \Gamma(1 / \nu)}, \quad \lambda \equiv\left(\frac{\Gamma(1 / \nu)}{4^{1 / \nu} \Gamma(3 / \nu)}\right)^{1 / 2}$$
\paragraph{Student-t Distribution}
$$f_S(\eta ; \nu) \equiv \frac{\Gamma\left(\frac{\nu+1}{2}\right)}{\sqrt{(\nu-2) \pi} \Gamma\left(\frac{\nu}{2}\right)}\left(1+\frac{\eta^2}{(\nu-2)}\right)^{-\frac{\nu+1}{2}}$$

@@

The Markov-switching GARCH specification we use follows \cite{ardia_markov-switching_2019}: 
Denote $y_t$ the log-returns in time period $t$, i.e. $log(p_t-p_{t-1})$ if $p_t$ is the asset price at time t.

@@

For training the model and producing the forecasts we use the R package 'MSGARCH' (version 2.50) by \cite{ardia_markov-switching_2019}.

@@

\subsubsection{Data set}
Our data set

The GARCH model assumes that the datapoints are equidistant in the time dimension, hence we will use the closing prices of the Index and model the close-to-close variance. Both for numerical reasons as well as for the ease of interpretation we will use the log-returns multiplied by 100 for training the model and for the evaluation.

@@

\subsection{Results}
\subsubsection{Model Selection}

\subsubsection{Analysis of Model Behaviour and Parameters}
In \cref{tab:model-params} the model parameters for the (MS-)GARCH model (see \cref{eq:GJR}) and shape parameters $\Psi = (\nu, \xi)$ of the conditional distribution (see ) are displayed, which were fitted using a maximum likelihood estimator on the training set. 
The two separate states from the MSGARCH model are denoted MSSR1 and MSSR2.
%TODO: Describe characteristics of MSSR1, MSSR2 and GARCH.
XXXX is likely to play a role after large volatility spikes like the 1987 Black Monday (see XXXX).

% latex table generated in R 4.1.2 by xtable 1.8-4 package
% Tue Sep 27 12:14:13 2022
\vspace{0.5cm}
\begin{minipage}[c]{0.5\textwidth}
	\begin{tabular}{rrrr}
		\hline
		& MSSR1 & MSSR2 & GARCH \\ 
		\hline
		$\alpha_{0,1}$ & 0.0042 & 0.1680 & 0.0082 \\ 
		$\alpha_{1,1}$ & 0.0214 & 0.0168 & 0.0356 \\ 
		$\alpha_{2,1}$ & 0.0781 & 0.2072 & 0.0741 \\ 
		$\beta_1$ & 0.9347 & 0.7483 & 0.9207 \\ 
		$\nu_1$ & 1.5314 & 1.0446 & 1.3168 \\ 
		$\xi_1$ & 0.9680 & 0.8731 & 0.9329 \\ 
		\hline
	\end{tabular}
	\captionof{table}{Fitted model and shape parameters.}
	 \label{tab:model-params}
\end{minipage}
\begin{minipage}[c]{0.5\textwidth}
	\begin{tabular}{lrr} 
		\hline
		& $t+1 | k=1$ & $t+1 | k=2$ \\
		\hline
		$t | k=1$ & 0.9983 & 0.0017 \\
		$t | k=2$ & 0.0059 & 0.9941 \\
		\hline
	\end{tabular}
	\captionof{table}{Transition probabilities of the MSGARCH states.}
 	\label{tab:trans-probs}
\end{minipage}
\vspace{0.5cm}

In \cref{tab:trans-probs} the transitions probabilities for the markov chain states in the MSGARCH model are displayed. The stable probabilities (i.e. the long-term probability of being in state 1 or 2) are XXXX for MSSR1 and XXXX for MSSR2.

@@

%TODO insample performance evaluation ?

\subsubsection{Out-of-Sample Evaluation}
We evaluated the performance of our model in an out-of-sample dataset ranging from \formatdate{02}{10}{2003} to \formatdate{19}{08}{2022}. For every date we produce point and density forecasts via simulation with a forecasting horizon ranging from 1 to 10 trading days.

@@

% TODO: Diebold-Mariano test

In \cref{fig:murphy-diagrams} the difference of the two forecasts in the murphy diagram are displayed. It can't be observed that any forecasting model dominates the other. This means that it depends on the error measure, whether the single-state GARCH or the MSGARCH forecasts produce smaller, more desireable quantities.
For an explanation of murphy diagrams, see \cite{ehm_quantiles_2016} Sections 3 and 4.

\begin{figure}[H]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.8\linewidth]{murph1.pdf}
		\caption{1a}
		\label{fig:sfig1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.8\linewidth]{murph2.pdf}
		\caption{1b}
		\label{fig:sfig2}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[width=.8\linewidth]{murph3.pdf}
	\caption{1b}
	\label{fig:sfig2}
\end{subfigure}
	\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[width=.8\linewidth]{murph4.pdf}
	\caption{1b}
	\label{fig:sfig2}
\end{subfigure}
	\caption{Plots showing the difference in the extremal scores of the MSGARCH and the GARCH forecasts for horizons 1-4.}
	\label{fig:murphy-diagrams}
\end{figure}

% TODO CRPS analysis

@@

\begin{appendices}
%TODO add tables here
\chapter{Point Forecasts}
\label{app:point-forecasts}
